Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-17 manuscript.tex
3.4

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extensions of Izhikevitch's polychronization model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
A notable extension of~\citep{izhikevich_polychronization_2006} is an extensive work aiming at reproducing the polychronization model~\citep{pauli_reproducing_2018}. Indeed, while the original paper contained material within the text to reproduce the whole model, it was not complete for the repoduction of all results presented in that manuscript. This more recent work details how this code was slighlty corrected. It comes with python code and a version control system detailing the whole process used to give provenance to the different steps in this scientific process.

@@

There are more applications to image processing using sparse spiking representations. Using the core computational unit defined, extension of the computation to a topographic representation similar to that observed in the primary visual cortex of mammals. design of micro-circuits with specific lateral interactions will allow us to design efficient micro-circuits for the sparse representation of images.

there are temporal delays in the nervous system, both at the neural~\citep{perrinet_active_2014}

and behavioral~\citep{khoei_flash-lag_2017} levels. Extending this knowledge to the optimization of delays in a SNN will provide a breakthrough in the efficiency of these networks.

may be used for motion detection and Motion-based prediction explains the role of tracking in motion extrapolation interpolation~\citep{kaplan_anisotropic_2013}~\citep{khoei_flash-lag_2017}

We will review some more applications of using precise spiking motifs in neuromorphic engineering, but will first review current evidence in neurobiology, that is, from actual recordings in biological tissues.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Precise spiking motifs in neurobiology}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 In Bellec~\citep{bellec_fitting_2021}, authors fit summary statistics of neural data with a differentiable spiking network simulator. The loss function is the cross entropy (following Bernouilli hypothesis with a GLM where each unit is modelled with a SRM neuron~\citep{gerstner_time_1995} with recurrent dynamics). The model uses samples and measure method sto include latent / hidden neurons. In particular, it    comes with  \href{code}{https://github.com/EPFL-LCN/pub-bellec-wang-2021-sample-and-measure}. It uses the publicly available \href{V1-dataset}{http://crcns.org/data-sets/vc/pvc-11}, which allows to supervise the model with the input being the movie and the output the spikes recorded.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extensions of Izhikevitch's polychronization model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
A notable extension of~\citep{izhikevich_polychronization_2006} is a very detailed work aiming at reproducing the polychronization model~\citep{pauli_reproducing_2018}. Indeed, while the original paper contained material within the text to reproduce the whole model, it was not complete for the repoduction of all results presented in that manuscript. This more recent work details how this code was slighlty corrected. It comes with python code and a version control system detailing the whole process used to give provenance to the different steps in this scientific process.

@@

%There are more applications to image processing using sparse spiking representations. Using the core computational unit defined, extension of the computation to a topographic representation similar to that observed in the primary visual cortex of mammals. design of micro-circuits with specific lateral interactions will allow us to design efficient micro-circuits for the sparse representation of images.
A predictive model defined in the framework of the free-energy principle was able to account for temporal delays in the nervous system, both at the sensory and motor levels~\citep{perrinet_active_2014}.  %
%and behavioral~\citep{khoei_flash-lag_2017} levels. Extending this knowledge to the optimization of delays in a SNN will provide a breakthrough in the efficiency of these networks.
Such a model was implemented at the network level by showing that motion-based prediction explains the role of tracking in motion extrapolation interpolation~\citep{khoei_motion-based_2013}. Note that this motion-based prediction is implemented in the weights of the neural network by defining connections between neurons with specific delays.  Two neurons which were selective to specific motions were connected if the delay was coherent with the change in the position of their respective receptive fields~\citep{hogendoorn_predictive_2019}. This was aso implemented in a spiking neural network and reproduced the observation that neural activty was maintained during the trajectory of a smoothly moving dot even if it was momentarily blanked~\citep{kaplan_anisotropic_2013}. This led in particular to the proposal that such delay-based computations could explain diverse perceptual mechanisms, such as the flash-lag illusion~\citep{khoei_flash-lag_2017}. 
We will review some more applications of using precise spiking motifs in neuromorphic engineering, but will first review current evidence in neurobiology, that is, from actual recordings in biological tissues.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Precise spiking motifs in neurobiology}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
 In Bellec~\citep{bellec_fitting_2021}, authors fit summary statistics of neural data with a differentiable spiking network simulator. The loss function is the cross entropy (following Bernouilli hypothesis with a GLM where each unit is modelled with a SRM neuron~\citep{gerstner_time_1995} with recurrent dynamics). The model uses samples and measure method sto include latent / hidden neurons. In particular, it    comes with  \href{code}{https://github.com/EPFL-LCN/pub-bellec-wang-2021-sample-and-measure}. It uses the publicly available \href{V1-dataset}{http://crcns.org/data-sets/vc/pvc-11}, which allows to supervise the model with the input being the movie and the output the spikes recorded.
